%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, 12pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{sansmathfonts}
\usepackage[T1]{fontenc}
\renewcommand{\familydefault}{\sfdefault}
%\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newpxtext} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\huge Avinash Iyer} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{\textbf{Email:} iyera@oxy.edu} % Your address
\moveleft.5\hoffset\centerline{\textbf{Phone:} (408) 203-8125}
\moveleft.5\hoffset\centerline{\textbf{Website:} blog.avinashiyer.xyz}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
\section{\sc About Me}
Collaborative, academically-adept undergraduate seeking PhD programs in analysis, with a particular interest in operator theory and operator algebras.
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\sc Education}

{\sl Bachelor of Arts} in Mathematics \hfill May 2025 (Expected) \\
GPA: 3.93\\
Occidental College, Los Angeles, CA 
%----------------------------------------------------------------------------------------
\section{\sc Relevant \\ Courses}

\textbf{Completed Courses:} Linear Algebra, Abstract Algebra, Topology, Graph Theory, Real Analysis, Real Analysis II (Metric Spaces and Measure Theory), Algebra II (Ring Theory, Field Theory, and Galois Theory), Complex Analysis.\\

\textbf{Planned Courses (Fall 2024):} Ordinary Differential Equations, Set Theory and the Foundations of Mathematics, Mathematical Methods in Physics, Advanced Linear Algebra, Amenability and $C^{\ast}$-Algebras (Honors Thesis independent study).\\

\textbf{Planned Courses (Spring 2025):} Partial Differential Equations, Numerical Analysis, Quantum Mechanics, Statistical Physics.
%----------------------------------------------------------------------------------------
\section{\sc Projects and Papers}
{\sl Research Experience for Undergraduates:} NSF-REU at Texas A\&M-Commerce, member of the Complex Analysis research group under Dr. Mehmet Celik, studying excess area identities under operators on particular function spaces.\\
\vspace{4pt}\\
{\sl Power BI Full Floor Dashboard:} project during internship at Onto Innovation, using Power Queries to harmonize different tool families' information, and used Synoptic Panel to visualize data.\\
\vspace{4pt}\\
{\sl Personal Website:} used GitHub Pages and Jekyll to create a website for a portfolio in college.\\
%{\sl Advent of Code:} honed problem-solving skills in Python.\\
%\vspace{4pt}\\
%{\sl Public Economics Policy Papers:} analyzed the expected effects of zoning reform in the first paper and tax reform that treated owner-occupied housing as equivalent to other forms of capital in the second paper. Drew on academic research and implementations to develop analysis.

\section{\sc Awards and Honors}
Dean's List\hfill Fall 2021--Spring 2024\\
President's Scholarship\hfill Fall 2021--Present\\
William Lowell Putnam Exam\hfill 1/120, 8/120

\section{\sc Work Experience}

%reverse chronological order, split into Relevant and Other experience
% 3–5 bullet points per segment: skills and results achieved

Section Editor \hfill September 2023--Present \\
\textit{The Occidental}
\begin{itemize}\itemsep -2pt
  \item Worked with senior team, co-editors, and writers to ensure high-quality opinion articles.
  \item Managed demanding weekly schedule while full-time student in upper division math and economics courses.
  \item Ensured all articles were harmonized with AP Style.
\end{itemize}

Staff Writer \hfill January 2022--Present \\
\textit{The Occidental} 
\begin{itemize} \itemsep -2pt
  \item Authored over 20 articles, including reported stories and opinions.
  \item Interviewed at least 3 sources per reported story, met demanding weekly schedule.
  \item Worked with editors to ensure high-quality story.
\end{itemize} 

{Data Analytics Intern} \hfill May 2023--August 2023 \\
\textit{Onto Innovation, Milpitas, CA}
\begin{itemize} \itemsep -2pt % Reduce space between items
  \item Worked on process development within Metrology Business Unit.
  \item Improved Power Automate workflows for process improvements across 3 product families.
  \item Integrated data sources from manufacturing plans and floor information to create Power BI reports that provided at-a-glance understanding of state of manufacturing.
\end{itemize}

Grader\hfill September 2022--May 2023\\
\textit{Mathematics and Economics Departments, Occidental College}
\begin{itemize}\itemsep -2pt
  \item Provided extensive feedback for student assignments in Intermediate Microeconomics and Calculus I.
  \item Maintained standards and deadlines alongside demanding class schedule and work for the newspaper.
\end{itemize}

%----------------------------------------------------------------------------------------
%	Specialized Skills
%---------------------------------------------------------------------------------------- 

\section{\sc Specialized \\ Skills} 

{\sl Languages:} Proficient in \LaTeX, have used SQL, Mathematica, Python, and R\\
{\sl Enterprise Software:} Microsoft Office and Microsoft Power Platform\\
{\sl Spatial Thinking and Reasoning}\\
{\sl Mathematics and Computation}
%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
