\documentclass[10pt]{extarticle}
\title{}
\author{}
\date{}
\usepackage[shortlabels]{enumitem}


%paper setup
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=1in}
\usepackage{fancyhdr}
% sans serif font:
\usepackage{cmbright}
%symbols
\usepackage{amsmath}
\usepackage{bigints}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{bbold}
\usepackage[hidelinks]{hyperref}
\usepackage{gensymb}
\usepackage{multirow,array}
\usepackage{multicol}

\newtheorem*{remark}{Remark}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

%chemistry stuff
%\usepackage[version=4]{mhchem}
%\usepackage{chemfig}

%plotting
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{cd}
\tikzset{middleweight/.style={pos = 0.5}}
%\tikzset{weight/.style={pos = 0.5, fill = white}}
%\tikzset{lateweight/.style={pos = 0.75, fill = white}}
%\tikzset{earlyweight/.style={pos = 0.25, fill=white}}

%\usepackage{natbib}

%graphics stuff
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage[style=numeric, backend=biber]{biblatex} % Use the numeric style for Vancouver
\addbibresource{ps4.bib}
%code stuff
%when using minted, make sure to add the -shell-escape flag
%you can use lstlisting if you don't want to use minted
%\usepackage{minted}
%\usemintedstyle{pastie}
%\newminted[javacode]{java}{frame=lines,framesep=2mm,linenos=true,fontsize=\footnotesize,tabsize=3,autogobble,}
%\newminted[cppcode]{cpp}{frame=lines,framesep=2mm,linenos=true,fontsize=\footnotesize,tabsize=3,autogobble,}

%\usepackage{listings}
%\usepackage{color}
%\definecolor{dkgreen}{rgb}{0,0.6,0}
%\definecolor{gray}{rgb}{0.5,0.5,0.5}
%\definecolor{mauve}{rgb}{0.58,0,0.82}
%
%\lstset{frame=tb,
%	language=Java,
%	aboveskip=3mm,
%	belowskip=3mm,
%	showstringspaces=false,
%	columns=flexible,
%	basicstyle={\small\ttfamily},
%	numbers=none,
%	numberstyle=\tiny\color{gray},
%	keywordstyle=\color{blue},
%	commentstyle=\color{dkgreen},
%	stringstyle=\color{mauve},
%	breaklines=true,
%	breakatwhitespace=true,
%	tabsize=3
%}
% text + color boxes
%\renewcommand{\mathbf}[1]{\mathbb{#1}}
%\usepackage[most]{tcolorbox}
%\tcbuselibrary{breakable}
%\tcbuselibrary{skins}
%\newtcolorbox{problem}[1]{colback=white,enhanced,title={\small #1},
%          attach boxed title to top center=
%{yshift=-\tcboxedtitleheight/2},
%boxed title style={size=small,colback=black!60!white}, sharp corners, breakable}
%including PDFs
%\usepackage{pdfpages}
\setlength{\parindent}{0pt}
\usepackage{cancel}
\pagestyle{fancy}
\fancyhf{}
\rhead{Avinash Iyer}
\lhead{Economics of Education: Problem Set 4}
\newcommand{\card}{\text{card}}
\newcommand{\ran}{\text{ran}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\iprod}[2]{\left\langle #1,#2\right\rangle}
\newcommand{\norm}[1]{\left\Vert #1\right\Vert}
\setcounter{secnumdepth}{0}
\begin{document}
  \section{Summary}%
  In Morton et al.'s paper, ``A multi-state, student-level analysis of the effects of the four-day school week on student achievement and growth,'' the authors examine the adoption of four-day school weeks --- which have become increasingly popular, especially in the post-COVID era, where schools find staffing increasingly difficult --- and its effects on students' academic achievement, in order to provide proper evaluation of the policy. The NWEA Measure of Academic Progress Growth exams are administered every fall, winter, and spring, which Morton et al. cite as a superior way to measure the effect of the four-day week on gains, as opposed to annual spring exams (which are confounded by the effects of summer vacation). As a result, the authors use a two-way fixed effects difference-in-difference estimate to examine the effects of adoption of a four-day week, using samples from six states (CO, IA, KS, MT, ND, and WY), as well as examine whether the effects of a four-day school week on gains are even across rural vs. non-rural districts, as well as on the basis of grades and particular subgroups. They find that school enrollment did not change significantly as a result of adoption (removing a potential source of bias), and after accounting for grade-term, school, and student fixed effects, find a statistically significant drop in fall-to-spring gains in both reading and math as a result of adoption of the four-day week. The drop in fall-to-spring gains was higher in non-rural school districts (at a stronger statistical significance) than in rural districts. At the same time, the authors do qualify some of their results --- it is possible that the four-day school week could allow for greater teacher retention (in which case, the positive effects of teacher retention could outweigh the negative effects on student achievement from lower instructional time), but such research has not been taken up yet.
  \section{Critique}%
  My impression is that the paper is very comprehensive and takes a much more thorough look at the effects of the four-day work week than the previous papers it cites. Using a standardized exam that is administered throughout the year (as opposed to once in the spring or fall) allows for a better measure of the true effects that the length of school instruction has on student achievement. Additionally, assessing gains (as opposed to changes or levels) is a much more appropriate measure of the effects on student achievement, as the particular measure of gains assesses the same student at the same school in the same year --- this purely isolates the effect of the instructional period length, rather than potentially catching factors that bias the perceived gains downward (or upward). The combination of these factors --- measuring within-year gains on a standardized exam --- suggests that the researchers have a plausible causal estimate of the effects of a four-day school week, which stands in contrast to previous attempts that did not successfully fully isolate the effects of adoption. At the same time, even if the paper documents a negative effect of the four-day week on student achievement, the researchers were also careful to note that the potential alternative (of lower teacher retention from maintaining the five-day week) could yield worse overall results for students than the four-day week; this consideration to potential alternatives shows that the researchers still maintain their epistemic humility, which I find quite admirable.
  \section{Discussion Questions}%
  \begin{itemize}
    \item What are some potential explanations for the heterogeneous effects of adoption of the four-day week between rural and non-rural school districts? Must there necessarily be convergence of effect size between rural and non-rural districts?
    \item What are some possible sources of selection bias in the effects of adoption on test scores, and how do the authors test for and mitigate such potential selection bias?
    \item Keeping the effect of the adoption of the four-day week on test scores in mind, what is a potential advantage of adoption relative to the most likely alternative?
  \end{itemize}
\end{document}
