\documentclass[10pt]{mypackage}

% sans serif font:
%\usepackage{cmbright}
%\usepackage{sfmath}
%\usepackage{bbold} %better blackboard bold

\usepackage{homework}
%\usepackage{notes}
\usepackage{newpxtext,eulerpx,eucal}
\renewcommand*{\mathbb}[1]{\varmathbb{#1}}

\fancyhf{}
\rhead{Avinash Iyer}
\lhead{Complex Analysis: Assignment 3}

\setcounter{secnumdepth}{0}

\begin{document}
\RaggedRight
\begin{problem}[Problem 1]\hfill
  \begin{enumerate}[(a)]
    \item Determine every holomorphic function $f\colon \C\rightarrow \C$ satisfying $\re\left( f\left( z \right) \right) = \re\left( z \right)^2 - \im\left( z \right)^2$.
    \item Let $f\colon \C\rightarrow \C$ be given by
      \begin{align*}
        f(z) &\coloneq \sqrt{\left\vert \re\left( z \right)\im\left( z \right) \right\vert}.
      \end{align*}
      Show that the Cauchy--Riemann equations are satisfied for $f$ at $z = 0$, but $f$ is not differentiable at $z = 0$.
  \end{enumerate}
\end{problem}
\begin{solution}\hfill
  \begin{enumerate}[(a)]
    \item We want to determine $f\colon \C\rightarrow \C$ such that
      \begin{align*}
        f\left( x + iy \right) &= u\left( x,y \right) + iv\left( x,y \right)
      \end{align*}
      satisfies
      \begin{align*}
        u\left( x,y \right) &= x^2 - y^2,
      \end{align*}
      and the Cauchy--Riemann equations:
      \begin{align*}
        \pd{u}{x} &= \pd{v}{y}\\
        \pd{u}{y} &= -\pd{v}{x}.
      \end{align*}
      First, we must verify that $u$ is indeed harmonic. This follows from the fact that
      \begin{align*}
        \pd{^2u}{x^2} &= 2\\
        \pd{^2u}{y^2} &= -2.
      \end{align*}
      Furthermore, we see that $u$ is $C^{3}$, as all of the third partial derivatives are equal to zero. Therefore, a harmonic conjugate of $u$ exists and ensures that $f$ is holomorphic on $\C$. By evaluating the Cauchy--Riemann equations separately, we find that
      \begin{align*}
        \pd{v}{y} &= 2x,
      \end{align*}
      or $ v = 2xy + K(x)$, and
      \begin{align*}
        -\pd{v}{x} &= -2y,
      \end{align*}
      or $v = 2xy + L(y)$. These are only in harmony when $v = 2xy + c$, where $c\in \C$ is a constant. Thus, we find that
      \begin{align*}
        f\left( x + iy \right) &= \left( x^2 - y^2 \right) + i\left( 2xy \right) + c
      \end{align*}
      is necessarily (up to a constant) unique.
    \item We write $f$ as
      \begin{align*}
        f\left( x + iy \right) &= \sqrt{\left\vert xy \right\vert}.
      \end{align*}
  \end{enumerate}
\end{solution}
\begin{problem}[Problem 2]
  Let $U\subseteq \C$ be a region, and let $f\colon U\rightarrow \C$ be a function.
  \begin{enumerate}[(a)]
    \item Suppose that $f$ and $ \overline{f} $ are both holomorphic. Show that $f$ is constant.
    \item Suppose that $f$ is holomorphic and $\re\left( f \right)$ is constant. Show that $f$ is constant.
  \end{enumerate}
\end{problem}

\end{document}
