\documentclass[10pt]{mypackage}

% sans serif font:
%\usepackage{cmbright}
%\usepackage{sfmath}
%\usepackage{bbold} %better blackboard bold

\usepackage{homework}
%\usepackage{notes}
\usepackage{newpxtext,eulerpx,eucal}
\renewcommand*{\mathbb}[1]{\varmathbb{#1}}

\fancyhf{}
\rhead{Avinash Iyer}
\lhead{Complex Analysis: Assignment 2}

\setcounter{secnumdepth}{0}

\begin{document}
\RaggedRight
\begin{problem}\hfill
  \begin{enumerate}[(a)]
    \item Show that the power series $\sum_{n=0}^{\infty}\frac{z^{n}}{n!}$ converges for all $z\in \C$, in which it defines an analytic function, which we denote $e^{z}$.
    \item With this as the definition of $e^{z}$, prove that $e^{z}e^{w} = e^{z+w}$.
    \item Show that for $\theta\in \R$, we have that $e^{i\theta} = \cos\left( \theta \right) + i\sin\left( \theta \right)$, where $\cos\left( \theta \right)$ and $\sin\left( \theta \right)$ are defined via their usual power series representations.
  \end{enumerate}
\end{problem}
\begin{problem}
  Let $U\subseteq \C$ be an open set, $f\colon U\rightarrow \C$ an analytic function. Since $f$ is analytic, given $z_0\in U$, there is $r > 0$ and a sequence $\left( a_n \right)_n$ such that $f(z) = \sum_{n=0}^{\infty}a_n\left( z-z_0 \right)^{n}$ for all $z\in U\left( z_0,r \right)$.\newline

  Suppose there exists $R > r$ such that $U\left( z_0,R \right) \subseteq U$ and $\sum_{n=0}^{\infty}a_n\left( z-z_0 \right)^{n}$ has radius of convergence at least $R$. Show that $f(z) = \sum_{n=0}^{\infty}a_n\left( z-z_0 \right)^{n}$ for all $z\in U\left( z_0,R \right)$.
\end{problem}
\begin{solution}
  On the connected open set $V = U\left( z_0,R \right)$, define
  \begin{align*}
    g(z) &= \sum_{n=0}^{\infty}a_n\left( z-z_0 \right)^{n}.
  \end{align*}
  Observe that $f|_{V}$ and $g$ agree on the open subset $U\left( z_0,r \right)\subseteq U\left( z_0,R \right)$. By the identity theorem, this means that $f = g$ on $U\left( z_0,R \right)$.
\end{solution}
\begin{problem}
  Let $U\subseteq \C$ be a region, and let $f\colon U\rightarrow \C$ be an analytic function.
  \begin{enumerate}[(a)]
    \item Suppose $f$ is nonconstant, $z_0\in U$. Show that there exists some $r > 0$ for which $U\left( z_0,r \right)\subseteq U$, a positive integer $k\in \N$, an analytic function $g\colon U\left( z_0,r \right)\rightarrow \C$, and a nonconstant $\lambda\in \C\setminus \set{0}$ such that for $z\in U\left( z_0,r \right)$,
      \begin{align*}
        f(z) &= f\left(z_0\right) + \lambda\left( z-z_0 \right)^{k} + \left( z-z_0 \right)^{k+1} g(z).
      \end{align*}
    \item Suppose that $f$ is nonconstant, and $z_0\in U$ is such that $f\left( z_0 \right) \neq 0$. Show that there exists some $s > 0$ such that $U\left( z_0,s \right)\subseteq U$, and $w_1,w_2\in U\left( z_0,s \right)$ such that $\left\vert f\left( w_1 \right) \right\vert > \left\vert f\left( z_0 \right) \right\vert > \left\vert f\left( w_2 \right) \right\vert$.
    \item Show that if $\left\vert f \right\vert$ is constant, then $f$ is constant.
  \end{enumerate}
\end{problem}
\begin{solution}\hfill
  \begin{enumerate}[(a)]
    \item Since $f$ is analytic, we may find $r > 0$ and a sequence $\left( a_n \right)_n$ such that
      \begin{align*}
        f(z) &= \sum_{n=0}^{\infty} a_n\left( z-z_0 \right)^{n}.
        \intertext{Observe that $f\left( z_0 \right) = a_0$, so}
             &= f\left( z_0 \right) + \sum_{n=1}^{\infty} a_n\left( z-z_0 \right)^{n}.
        \intertext{Next, we find the minimum value of $n$ such that $a_n\neq 0$, which we define to be $k$. Such a value must exist since $f$ is a nonconstant function. This gives}
             &= f\left( z_0 \right) + a_k\left( z-z_0 \right)^{k} + \sum_{n=k+1}^{\infty}a_n\left( z-z_0 \right)^{n}.
             \intertext{Finally, by reindexing the sum and factoring out $\left( z-z_0 \right)^{k+1}$, we get}
             &= f\left( z_0 \right) + a_k\left( z-z_0 \right)^{k} + \left( z-z_0 \right)^{k+1}\sum_{n=0}^{\infty}a_{n+k+1}\left( z-z_0 \right)^{n}.
        \intertext{Define $g(z)$ to be equal to the sum, and define $\lambda = a_k$. Notice that since the radius of convergence of a power series is a limiting case, $g$ and $f$ have the same radius of convergence. This gives}
             &= f\left( z_0 \right) + \lambda \left( z-z_0 \right)^{k} + \left( z-z_0 \right)^{k+1}g(z).
      \end{align*}
    \item Let $f$ be a nonconstant analytic function with $f\left( z_0 \right) \neq 0$. Since $f$ is nonconstant, we see that $\lambda$ in the previous problem is nonzero, meaning that $\left\vert \lambda \right\vert$ is nonzero, in addition to $\left\vert f\left(z_0\right) \right\vert$.
  \end{enumerate}
\end{solution}
\end{document}
