\documentclass[10pt]{package2}

\usepackage{cmbright,sfmath,bbold}
\renewcommand{\mathcal}{\mathtt}
\setcounter{chapter}{-1}
%\usepackage{newpxtext,eulerpx,eucal}
\usepackage{titlesec}
\usepackage[backend=biber,style=alphabetic,sorting=ynt]{biblatex}
\addbibresource{chapters/references.bib}
\DeclareMathOperator{\op}{op}
\DeclareMathOperator{\sa}{s.a.}
%\renewcommand{\coloneq}{=}
\title{Characterizing Amenability in Discrete Groups\\{\large A Tour of Algebra and Analysis}}
\author{Avinash Iyer}
\date{\today}
\usepackage{microtype}
\hbadness=10000
\usepackage[hidelinks]{hyperref}
\begin{document}
\maketitle
\RaggedRight
\tableofcontents
%\part{Prelude}
\chapter{Introduction}
A lot of texts in mathematics have an unfortunate tendency to be quite dull. Now, of course, this is in part because the subject matter is not generally a laughing one --- and amenability is, despite my best efforts, sadly no exception. However, regardless, amenability is a fascinating topic, in large part because it blends algebra and analysis in a way that a sufficiently advanced undergraduate, or, at least, someone like me, can understand and glean fascinating insights from. I hope that, in so doing, this thesis will be of great use to at least one individual in furthering their understanding of the topic and deepening their understanding of analysis and algebra meanwhile. The choice to employ humor when appropriate was entirely my own, and, rather than a lack of respect for the readers of the text, I believe it reflects the deepest respect possible that I have for those who read my work. There is no higher expression of service than making one smile while they find edification in the depths of abstract mathematics.\newline

The general outline for this thesis is as follows.
\begin{itemize}
  \item Chapter 1: here, I construct a variety of free objects (such as free groups, free vector spaces, and free algebras), with the minimal necessary background covered in Appendix \ref{ch:algebra_and_linear_algebra}.
  \item Chapter 2: here, we cover the motivating example for the topic of amenability. Following the exposition in \cite{lectures_on_amenability} and \cite{amenable_banach_algebras}, I explain and prove the Banach--Tarski paradox in its most general form. John von Neumann would later develop the study of amenability using the Banach--Tarski paradox.
  \item Chapter 3: following with the exposition in \cite{lectures_on_amenability} and \cite{amenable_banach_algebras}, and featuring a proof of a fact in graph theory concocted by yours truly with the help of \cite{marshall_hall_thm}, we prove that non-paradoxicality is a necessary \textit{and} sufficient condition for a group to be amenable. This is our first insight into the connection between the Banach--Tarski paradox --- which is related to the action of the group $\text{E}(3)$ on $\R^3$ --- and the underlying algebraic structure.
  \item Chapter 4: now, we are prepared to introduce a more analytic understanding of amenability. We show the equivalence between the definition of amenability --- the existence of a translation-invariant finitely additive probability measure on the $\sigma$-algebra $P(G)$ --- and the existence of a special linear functional on the space of all bounded functions on the group with codomain $\C$ (or $\R$). Using this property, we are able to establish the amenability of a wide class of groups, such as all the abelian groups and solvable groups.
  \item Chapter 5: we develop a different characterization of amenability using a more combinatorial characterization for amenability --- the Følner condition. After developing the Følner condition, we prove that the Følner condition is equivalence to the existence of an approximate mean, which is equivalent to the existence of a mean (or invariant state). We then apply the Følner condition to establish the amenability of another wide class of groups that often appear in geometric group theory --- the groups of subexponential growth.
\end{itemize}
\chapter{Categorical Constructions for the Unemployed Mathematician}\label{ch:categorical_constructions}
\input{chapters/categorical_constructions.tex}
% Here, will speedrun through free groups, free vector spaces, tensor products, free algebras, and the group *-algebra. We will discuss the free group in chapter 2, and the rest in chapter 8 when elaborating on nuclearity.
\chapter{How to Feed 5,000 Hungry Mathematicians: Paradoxical Decompositions}\label{ch:paradoxical_decompositions}
\input{chapters/paradoxical_decompositions.tex}
%\part{Fugue}
\chapter{Resolving A Paradox: Tarski's Theorem}\label{ch:tarskis_theorem}
\input{chapters/tarskis_theorem.tex}
\chapter{Amenability through Invariant States}\label{ch:invariant_states}
\input{chapters/invariant_states.tex}
% need snappy name for this too
\chapter{Følner's Condition and Approximate Means}\label{ch:folner_condition}
\input{chapters/folner_condition.tex}
% Testing names: Engineering a Mean: Følner's Condition and Approximate Means
\chapter{The Left-Regular Representation, Kesten's Criterion, and Hulanicki's Criterion}\label{ch:left_regular_representation}
% need snappy name
\chapter{The Nuclear Option: Amenability in \texorpdfstring{$C^{\ast}$-Algebras}{C*-Algebras}}\label{ch:nuclearity}
% need snappy name
\appendix
\chapter{Algebra and Linear Algebra}\label{ch:algebra_and_linear_algebra}
\input{chapters/algebra_and_linear_algebra.tex}
% Here, will discuss group theory, results like FIT/normal subgroups and the fundamental theorem for finite/finitely generated abelian groups, ring theory (homomorphisms, ideals and maximal ideals, quotient rings, etc.), abstract linear algebra (vector spaces, bases, linear functionals), algebras (definitions, homomorphisms, unitizations)
\chapter{Point-Set Topology}\label{ch:point_set_topology}
\input{chapters/point_set_topology.tex}
\chapter{Measure Theory and Integration}\label{ch:measure_theory}
\input{chapters/measure_theory.tex}
% I can trim down this section quite a lot
\chapter{Functional Analysis}\label{ch:functional_analysis}
\input{chapters/functional_analysis.tex}
% Get rid of the purely algebraic content in here, only focus on the analysis.
\nocite{*}
\printbibliography
\end{document}
