\documentclass[8pt]{extarticle}
\title{}
\author{}
\date{}
\usepackage[shortlabels]{enumitem}


%paper setup
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=1in}
\usepackage{fancyhdr}
% sans serif font:
\usepackage{cmbright}
%symbols
\usepackage{amsmath}
\usepackage{bigints}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{gensymb}
\usepackage{multirow,array}
\usepackage{multicol}

\newtheorem*{remark}{Remark}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

%chemistry stuff
%\usepackage[version=4]{mhchem}
%\usepackage{chemfig}

%plotting
\usepackage{pgfplots}
\usepackage{tikz}
\tikzset{middleweight/.style={pos = 0.5}}
%\tikzset{weight/.style={pos = 0.5, fill = white}}
%\tikzset{lateweight/.style={pos = 0.75, fill = white}}
%\tikzset{earlyweight/.style={pos = 0.25, fill=white}}

%\usepackage{natbib}

%graphics stuff
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage[style=numeric, backend=biber]{biblatex} % Use the numeric style for Vancouver
\addbibresource{the_bibliography.bib}
%code stuff
%when using minted, make sure to add the -shell-escape flag
%you can use lstlisting if you don't want to use minted
%\usepackage{minted}
%\usemintedstyle{pastie}
%\newminted[javacode]{java}{frame=lines,framesep=2mm,linenos=true,fontsize=\footnotesize,tabsize=3,autogobble,}
%\newminted[cppcode]{cpp}{frame=lines,framesep=2mm,linenos=true,fontsize=\footnotesize,tabsize=3,autogobble,}

%\usepackage{listings}
%\usepackage{color}
%\definecolor{dkgreen}{rgb}{0,0.6,0}
%\definecolor{gray}{rgb}{0.5,0.5,0.5}
%\definecolor{mauve}{rgb}{0.58,0,0.82}
%
%\lstset{frame=tb,
%	language=Java,
%	aboveskip=3mm,
%	belowskip=3mm,
%	showstringspaces=false,
%	columns=flexible,
%	basicstyle={\small\ttfamily},
%	numbers=none,
%	numberstyle=\tiny\color{gray},
%	keywordstyle=\color{blue},
%	commentstyle=\color{dkgreen},
%	stringstyle=\color{mauve},
%	breaklines=true,
%	breakatwhitespace=true,
%	tabsize=3
%}
% text + color boxes
\renewcommand{\mathbf}[1]{\mathbold{#1}}
\usepackage[most]{tcolorbox}
\tcbuselibrary{breakable}
\tcbuselibrary{skins}
\newtcolorbox{problem}[1]{colback=white,enhanced,title={\small #1},
          attach boxed title to top center=
{yshift=-\tcboxedtitleheight/2},
boxed title style={size=small,colback=black!60!white}, sharp corners, breakable}
%including PDFs
%\usepackage{pdfpages}
\setlength{\parindent}{0pt}
\usepackage{cancel}
\pagestyle{fancy}
\fancyhf{}
\rhead{Avinash Iyer}
\lhead{Math 400: Homework 9}
\newcommand{\card}{\text{card}}
\newcommand{\ran}{\text{ran}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\begin{document}
  \begin{problem}{Problem 1}
    True or false: If $H$ is a minor of $G$, then $H$ is a contraction of a subgraph of $G$.
    \tcblower
    True.
  \end{problem}
  \begin{problem}{Problem 2}
    Prove each of the following.
    \begin{enumerate}[(a)]
      \item There exists an infinite family $F$ of graphs such that no graph in $F$ is a subgraph of another graph in $F$.
      \item There exists an infinite family $F$ of graphs such that no graph in $F$ is a contraction of another graph in $F$.
      \item There exists an infinite family $F$ of graphs such that no graph in $F$ is a subgraph or a contraction of another graph in $F$.
    \end{enumerate}
    \tcblower
    \begin{problem}{(a)}
      Cycles; if we delete any vertex or edge of any cycle, then the degree of at least two vertices is reduced by $1$, while all vertices in every cycle are of degree $2$.
    \end{problem}
    \begin{problem}{(b)}
      The family of graphs $K_{2,n}$:
      \begin{center}
        \begin{tikzpicture}
          \draw (0,1) -- (-2,0);
          \draw (0,1) -- (-1,0);
          \draw (0,1) -- (0,0);
          \draw (0,1) -- (2,0);
          \draw (0,1) -- (1,0);
          \draw (0,-1) -- (-2,0);
          \draw (0,-1) -- (-1,0);
          \draw (0,-1) -- (0,0);
          \draw (0,-1) -- (2,0);
          \draw (0,-1) -- (1,0);
          \filldraw[red] (0,1) circle (2pt)
                (0,-1) circle (2pt);
          \filldraw[blue] (-2,0) circle (2pt)
                          (-1,0) circle (2pt)
                          (0,0) circle (2pt)
                          (1,0) circle (2pt)
                          (2,0) circle (2pt);
        \end{tikzpicture}
      \end{center}
    \end{problem}
  \end{problem}
  \begin{problem}{Problem 3}
    Prove that the set of all planar graphs is minor-closed.
    \tcblower
    Let $G$ be any planar graph. Then, by Wagner's theorem, it must be the case that neither $K_{5}$ nor $K_{3,3}$ are minors of $G$. Therefore, any minor of $G$, $G'$, must also not have $K_{5}$ nor $K_{3,3}$ as a minor --- otherwise, we would take the steps to create $G'$, then the steps to create one of the forbidden minors, and $G$ would have the forbidden minors as a minor.\\

    Thus, since no minor of any planar graph can be non-planar, it must be the case that planarity is minor-closed.
  \end{problem}
  \begin{problem}{Problem 4}
    Let $P$ be an arbitrary set of graphs. Let $P'$ be the set of all graphs not in $P$. By the Graph Minor Theorem, $P$ has a finite subset $F$ of graphs that are minor-minimal in $P$. Similarly, $P'$ has a finite subset $F'$ of graphs that are minor minimal in $P'$. Prove that if $P$ is minor-closed, then a graph $G$ is in $P'$ if and only if $G$ has a minor in $F'$. So, if $P$ is minor-closed, then $P$ and $P'$ are both ``characterized'' by $F'$. In fact, if $P$ is minor-closed, then $F$ consists of only one graph, namely the graph with only one vertex. Why?
    \tcblower
    Suppose $P$ is minor-closed. Then, if $H\in F$, then no minor of $H$ is in $P$ or $F$. 
    \begin{description}
      \item[$(\Rightarrow)$] Let $G\in P$. Suppose toward contradiction that there is a graph $H\in F'$ that is a minor of $G$.\\

        Since $P$ is minor-closed, and $H$ is a minor of $G\in P$, $H\in P$.\\

        However, $H\in F'\subseteq P'$. So, $H\in P$ and $H\in P'$. $\bot$
      \item[$(\Leftarrow)$] Suppose that no graph in $F'$ is a minor of $G$. Suppose toward contradiction that $G \notin P$.\\

        Then, $G\in P'$.\\

        So, by definition of $F'$, $G$ must have a minor in $F'$.\\

        So, $\exists H\in F'$ such that $H$ is a minor of $G$. $\bot$
    \end{description}
    Since any graph that is in $F$ must have a minor that is also in $F$, every graph in $F$ must reduce to the graph of one vertex.
  \end{problem}
  \begin{problem}{Problem 5}
    A graph $G$ is apex if $G-v$ is planar for some vertex $v$ of $G$. Prove that the set of apex graphs is minor-closed.
    \tcblower
    Let $G$ be an apex graph. Then, $\exists v\in V(G)$ such that $G-v$ does not contain either of the forbidden minors of planarity --- i.e., $G-v$ does not reduce to either $K_5$ or $K_{3,3}$.\\

    If $G'$ is a minor of $G$ formed via a process that includes deleting $v$, then $G'$ must be apex (as all planar graphs are apex, since they do not contain any of the forbidden minors) --- if $G'$ does not delete $v$ in the process of forming it from $G$, then $G' - v$ is a minor of $G'$ and of $G$, and since $G - v$ does not contain any of the forbidden minors , neither must $G' - v$. Therefore, $G' - v$ is apex.
    \end{problem}
    \begin{problem}{Problem 6}
      Prove that if $G$ is a connected graph, then for every edge $e$, $G-e$ has at most two connected components.
      \tcblower
    Since $G$ is connected, $\exists$ a path $P = (v,v_1,\dots,a,b,\dots,v_n,w)$ in $G$. It must be the case that $e\in P$, or else $P\in G-e$.\\

    Let $x\in V(G-e)$ such that $x\neq v$ and $x\neq w$. We will show that $\exists$ a path in $G-e$ from $x$ to $v$ or $x$ to $w$.\\

    Let $P_{xa}$ be a path in $G$ from $x$ to $a$. If $e\notin P_{xa}$, then $(v,\dots,a) \cup P_{xa}$ is a path from $v$ to $x$ without $e$.\\

    If $e\in P_{xa}$, then $P_{xa} = (x,\dots,b,a)$. So, $(x,\dots,b) \cup (b,\dots,w)$ is a path from $x$ to $w$ without $e$.
  \end{problem}
  \begin{problem}{Problem 7}
    In this problem, we (try to) prove Robbins' Theorem.
    \tcblower
    We will use induction on the number of edges to prove. Clearly, the statement holds for $|E(G)| = 3$. Suppose $|E(G)| > 3$ and the statement holds for every graph with fewer than $|E(G)|$ edges.
    \begin{enumerate}[(a)]
      \item Let $e\in G$. If $G-e$ is bridgeless, then by the inductive hypothesis, $G-e$ admits an orientation in which every distinct pair of vertices is within a directed circuit. So, if we add $e$ back into the graph, this does not change the fact that every distinct pair of vertices is in a circuit with the given orientation of $G-e$. Therefore, $G$ is circuit-oriented.
      \item If $G-e$ has a bridge, $e'$. We showed in the previous problem that deleting a bridge yields exactly two components --- thus, it must be the case that $G-e-e'$ contains two components.\\

        Since there is only one bridge in $G-e$, each of $G_1$ and $G_2$ must be bridgeless, meaning there is a circuit orientation in each component. Additionally, it must be the case that $e'$ has one endpoint in $G_1$ and one endpoint in $G_2$ --- if, WLOG, both of the endpoints of $e'$ were in $G_1$, then $e'$ would not be a bridge. Finally, if both endpoints of $e$ were in, WLOG, $G_1$, then $G-e$ would still contain the bridge $e'$, violating the assumption.
      \item Let $C = (v_1',v_2',w_1,\dots,w_k,v_1')$ be a circuit in $G$. Let $v_1,v_1'\in G_1$, $v_2,v_2'\in G_2$, where $e$ has endpoints $v_1$ and $v_2$, while $e'$ has endpoints $v_1'$ and $v_2'$. Since $C$ traverses $v_1'v_2'$, in $G - e$ it must be the case that $v_1'v_2'$ is the bridge between $G_1$ and $G_2$. So, $C$ traverses through various edges in $G_2$ --- however, since $C$ is a circuit that includes $v_1'$, it must be the case that $C$ traverses an edge between $G_2$ and $G_1$ --- this must be $e = v_2v_1$. If it were not $e$, then $G - e$ would not be bridgeless, as there would be another edge $x_2x_1$ from $G_2$ to $G_2$ contained in $C$, implying that $G - e - x_2x_1$ was still connected.
      \item Case 1: If $x,y$ are in the same $G_i$, then since the particular $G_i$ is bridgeless, there is a circuit orientation in $G_i$, meaning $x$ and $y$ are in the same directed circuit.\\

        Case 2: If $x\in G_1$ and $y\in G_2$, where $xy\neq e$, then $x$ and $y$ are distinct vertices in $G/e$. We trace out the circuit in $G_1$ from $x$ to $v_1'$, then $e'$, then the circuit in $G_2$ from $v_2'$ to $y$ to the vertex $v$ from contracting $v_2v_1$ in $G/e$. Finally, we trace along the circuit in $G_1$ from $v$ to $x$. This is a directed circuit.\\

        I don't know how to show Case 3.
    \end{enumerate}
  \end{problem}
  \begin{problem}{Problem 8}

  \end{problem}
  \begin{problem}{Problem 9}
    
  \end{problem}
  \begin{problem}{Problem 10}
    Prove Theorem 10.2 and Corollary 10.3. (I'm sorry, I'm doing this at like 10pm on the day before it was due because of various time constraints, it's very sloppy).
    \tcblower
    \begin{description}
      \item[Theorem 10.2:] If $G$ is a planar graph of order $n\geq 3$ and size $m$, then for $G$ to be planar, it must be the case that
        \begin{align*}
          n - m + r &=2.
          \shortintertext{In the maximal case, every edge is double-counted in finding the number of faces, and each face is a triangle, meaning that $3r \leq 2m$. So,}
          3n - 3m + 2m &\leq 6\\
          m &\leq 3n - 6
        \end{align*}
      \item[Corollary 10.3:] Suppose every vertex in $G$ is of degree $6$ or greater. Then, $|V(G)| \geq 7$, meaning
        \begin{align*}
          2m &= \sum d(v)\\
          &\geq 6|V(G)|\\
          m &\geq 3|V(G)|
        \end{align*}
    \end{description}
  \end{problem}
\end{document}
