\documentclass[8pt]{extarticle}
\title{}
\author{Avinash Iyer}
\date{}
\usepackage[shortlabels]{enumitem}

%font setup
%
\usepackage{newpxtext,eulerpx}

%paper setup
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=1in}
\usepackage{fancyhdr}

%symbols
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{gensymb}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

%chemistry stuff
\usepackage[version=4]{mhchem}
\usepackage{chemfig}

%plotting
\usepackage{pgfplots}
\usepackage{tikz}
\tikzset{middleweight/.style={pos = 0.5, fill=white}}
\tikzset{weight/.style={pos = 0.5, fill = white}}
\tikzset{lateweight/.style={pos = 0.75, fill = white}}
\tikzset{earlyweight/.style={pos = 0.25, fill=white}}

%\usepackage{natbib}

%graphics stuff
\usepackage{graphicx}
\graphicspath{ {./images/} }

%code stuff
%when using minted, make sure to add the -shell-escape flag
%you can use lstlisting if you don't want to use minted
%\usepackage{minted}
%\usemintedstyle{pastie}
%\newminted[javacode]{java}{frame=lines,framesep=2mm,linenos=true,fontsize=\footnotesize,tabsize=3,autogobble,}
%\newminted[cppcode]{cpp}{frame=lines,framesep=2mm,linenos=true,fontsize=\footnotesize,tabsize=3,autogobble,}

\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
	language=Java,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3
}
% text + color boxes
\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\newtcolorbox{problem}[1]{colback = white, title = {#1}, breakable}
\newtcolorbox{solution}{colback = white, colframe = black!75!white, title = Solution, breakable}
%including PDFs
\usepackage{pdfpages}
\setlength{\parindent}{0pt}

\pagestyle{fancy}
\fancyhf{}
\rhead{Avinash Iyer}
\lhead{Math 310: Class Notes}
\begin{document}{
  \begin{problem}{Introduction: naive set theory}
    \begin{align*}
      \mathbb{N} &= \{1,2,3,\dots,\}\\
      \mathbb{Z} &= \{0,\pm1,\pm2,\dots,\} \\
      \mathbb{Z}_+ &= \{0,1,2,\dots,\}\\
      \mathbb{Q} &= \left\{\frac{a}{b} \mid a,b\in\mathbb{Z},b\neq 0\right\}\\
      \mathbb{C} &= \{a+bi \mid a,b\in \mathbb{R}\}\\
      \mathbb{C}_q &= \{a+bi \mid a,b\in \mathbb{Q}\}
    \end{align*}
    Recall: given sets $X$ and $Y$, a relation from $X$ to $Y$ is a subset of $X\times Y$, where $\times$ denotes the cartesian product of $X$ and $Y$.\\

    A relation $f\subseteq X\times Y$ is a function from $X$ to $Y$ such that $\forall x\in X$, $\exists!y\in Y$ such that $(x,y) \in f$. We write $f(x) = y$, and denote $f$ as $f:X\rightarrow Y$.\\

    $X$ is the \textbf{domain} of $f$ and $Y$ is the \textbf{codomain}. The range $\textrm{Ran}(f) = \{f(x)\mid x\in X\}\subseteq Y$. \\

    The graph of a function $\textrm{Graph}(f) = \{(x,f(x))\mid x\in X\} \subseteq X\times Y$.
    \begin{problem}{Examples}
      \[\textrm{id}_x: X\rightarrow X, \textrm{id}_X(x) = x\]
      This is the identity function.\\

      The Characteristic Function: If $A\subseteq X$
      \[\mathbf{1}_A: X\rightarrow \mathbb{R}, ~\mathbf{1}_A(x) = \begin{cases}
        1,&x\in A\\
        0,&x\notin A
      \end{cases}\]
    \end{problem}
    \begin{problem}{Algebra of Functions}
      Let $X$ be any set, and $\mathcal(X;\mathbb{R}) = \{f:X\rightarrow \mathbb{R}\}$ represent the function space of $X$ with codomain $\mathbb{R}$.\\

      Let $f,g\in \mathcal{F}(X;\mathbb{R})$. Then, $(f+g)(x) = f(x) + g(x)$, and $(f\cdot g)(x) = f(x)\cdot g(x)$.\\

      If $t\in \mathbb{R}$, then $(tf)(x) = tf(x)$ (scalar multiplication). If $g(x)\neq 0\forall x\in X$, then $\left(\frac{f}{g}\right)(x) := \frac{f(x)}{g(x)}$.\\

      Finally, we have composition. If $f:X\rightarrow Y$ and $g:Y\rightarrow Z$ are functions, then $g\circ f(x) = g(f(x))$.
    \end{problem}
    \begin{problem}{Injective, Subjective, and Bijective}
      A function $f:X\rightarrow Y$ is a \textbf{injective} map, then, if $f(x_1) = f(x_2)$, then $x_1 = x_2$.For example, the shift map $S:\mathbb{N} \rightarrow \mathbb{N},~S(n) = n+1$ is injective.\\

      Any strictly increasing function $f:I\rightarrow \mathbb{R}$, where $I$ is any interval, is injective.\\

      A function $f$ is \textbf{surjective} if $\forall y\in Y, \exists x\in X$ such that $f(x) = y$.\\

      Consider the function $f:\mathbb{R} \rightarrow \mathbb{R},~f(x) = x^3-2x+1$. We can show that this function is surjective because $\lim_{x\rightarrow \infty}f(x) = \infty$, $\lim_{x\rightarrow -\infty} f(x) = -\infty$. Due to the intermediate value theorem, we get that $\textrm{Ran}(f) = \mathbb{R}$.\\

      $f$ is \textbf{bijective} if it is injective and surjective.
    \end{problem}
    \begin{problem}{Invertibility}
      Let $f:X\rightarrow Y$ be a function. $f$ is \textbf{left-invertible} if $\exists g:Y\rightarrow X$ such that $g\circ f = \textrm{id}_X$. $f$ is \textbf{right-invertible} if $\exists h:Y\rightarrow X$ such that $f\circ h = \textrm{id}_Y$.\\

      $f$ is \textbf{invertible} if $\exists k:Y\rightarrow X$ such that $f\circ k = \textrm{id}_Y$ and $k\circ f = \textrm{id}_X$.\\

      \begin{problem}{Proposition}
        $f$ is invertible if and only if $f$ is left and right invertible.
        \tcblower
          Forward direction: This is via the definition of invertibility.\\

          Reverse direction: Suppose $g$ is a left-inverse of $f$, and $h$ is a right-inverse of $f$. Therefore, $g\circ f = \textrm{id}_X$, and $f\circ h = \textrm{id}_Y$. Observe that $g = g\circ \textrm{id}_Y$. Therefore, $g = g\circ(f\circ h)$. Via associativity, $g = (g\circ f)\circ h = \textrm{id}_X \circ h = h$.
      \end{problem}
      \begin{problem}{Theorem}
        If $f:X\rightarrow Y$ is a function:
        \begin{enumerate}
          \item $f$ is injective $\Leftrightarrow$ $f$ is left-invertible.
          \item $f$ is surjective $\Leftrightarrow$ $f$ is right-invertible.
          \item $f$ is bijective $\Leftrightarrow$ $f$ is invertible.
        \end{enumerate}
        \tcblower
        We will prove the first proposition in the forward direction. Suppose $f$ is injective. Given $y\in \textrm{Ran}(f)$, we know that $\exists! x_y\in X$ such that $f(x_y) = Y$, by the definition of injective.\\

        Let $g:Y\rightarrow X$. We will define $g$ as follows:
        \[
          g(y) = \begin{cases}
            x_y & y\in \textrm{Ran}(f) \\
            x_0 & y\notin \textrm{Ran}(f)
          \end{cases}
        \] 
        Where $x_0$ is an arbitrary point in $X$. We can see that $g\circ f = \textrm{id}_X$.
      \end{problem}
      For example, the function $\textrm{Sin}(x)$ defined as $\sin(x)$ restricted to $[-\pi/2,\pi/2]$ has an inverse, $\arcsin(x):[-1,1] \rightarrow [-\pi/2,\pi/2]$.
    \end{problem}
  \end{problem}
}\end{document}
