\documentclass[10pt]{mypackage}

%\usepackage{mlmodern}
%\usepackage{newpxtext,eulerpx,eucal}
%\renewcommand*{\mathbb}[1]{\varmathbb{#1}}

%\usepackage{homework}
\usepackage{notes}

\usepackage[ backend=bibtex, style = alphabetic, sorting=ynt ]{biblatex}
\addbibresource{all_references.bib}

\usepackage{parskip}

\fancyhf{}
\fancyhead[R]{Avinash Iyer}
\fancyhead[L]{Countable Borel Equivalence Relations}
\fancyfoot[C]{\thepage}

\setcounter{secnumdepth}{0}

\begin{document}
\RaggedRight
\section{Orbit Equivalence}%
We will assume that $\left( X,\mu \right)$ is a nonatomic standard Borel probability space (i.e., a Borel probability space over a separable completely metrizable space $X$).
\subsection{Basics and Definitions}%
\begin{definition}
  A \textit{countable Borel equivalence relation} $\mathcal{R}\subseteq X\times X$ is a Borel subset and equivalence relation satisfying the assumption that
  \begin{align*}
    \left[ x \right]_{\mathcal{R}} &\coloneq \set{y\in X | \left( x,y \right)\in \mathcal{R}} 
  \end{align*}
  is countable.
\end{definition}
The set $\left[ \mathcal{R} \right]$ is known as the \textit{full group} of the equivalence relation $\mathcal{R}$ and consists of all Borel isomorphisms $\phi\colon X\rightarrow X$ with its graph satisfying $\operatorname{graph}\left(\phi\right)\subseteq \mathcal{R}$.

The set of all \textit{partial} Borel isomorphisms $\phi\colon \operatorname{dom}\left( \phi \right)\rightarrow \operatorname{ran}\left( \phi \right)$ with $\operatorname{graph}\left( \phi \right)\subseteq \mathcal{R}$ will be denoted $\left[ \left[ \mathcal{R} \right] \right]$.

The most basic example of a countable Borel equivalence relation is the space of orbits from the action of a countable discrete group $\Gamma\curvearrowright X$. We will write this as $\mathcal{R}\left( \Gamma\curvearrowright X \right)$. From now on, we will use ``equivalence relation'' to refer to countable Borel equivalence relations.

In fact, one can show that all such equivalence relations arise in this form.
\begin{theorem}[Feldman--Moore Theorem]
  If $\mathcal{R}$ is a countable Borel equivalence relation on $X$, then there exists a countable group $\Gamma$ and a Borel action $\Gamma\curvearrowright X$ such that $\mathcal{R} = \mathcal{R}\left( \Gamma\curvearrowright X \right)$. Moreover, both $\Gamma$ and the action can be chosen such that $\left( x,y \right)\in \mathcal{R}$ if and only if there is $g\in \Gamma$ with order $2$ such that $y = g\cdot x$.
\end{theorem}
We say the measure $\mu$ on $X$ is $\mathcal{R}$-invariant if
\begin{align*}
  \phi_{\ast}\mu &= \mu
\end{align*}
for all $\phi\in \left[ \mathcal{R} \right]$, where $\phi_{\ast}\mu\left( U \right) = \mu\left( \phi^{-1}\left( U \right) \right)$ for all Borel $U\subseteq X$.
\begin{proposition}
  The following are equivalent:
  \begin{enumerate}[(a)]
    \item $\mu$ is $\mathcal{R}$-invariant;
    \item $\mu$ is invariant under any $\Gamma$ where $\Gamma$ is such that $\mathcal{R} = \mathcal{R}\left( \Gamma\curvearrowright X \right)$;
    \item $\mu$ is $\Gamma$-invariant for some $\Gamma$ with $ \mathcal{R} = \mathcal{R}\left( \Gamma\curvearrowright X \right) $;
    \item for all $\phi\in \left[ \left[ \mathcal{R} \right] \right]$, we have $\mu\left( \operatorname{dom}\left( \phi \right) \right) = \mu\left( \operatorname{ran}\left( \phi \right) \right)$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  We have (d) implies (a) since $\left[ \left[ \mathcal{R} \right] \right]\supseteq \left[ \mathcal{R} \right]$, while (a) implies (b) since the action of $g$ is an element of $\left[ \mathcal{R} \right]$, and (b) implies (c) by definition. To see (c) implies (d), if $A = \operatorname{dom}\left( \phi \right)$ and $B = \operatorname{ran}\left( \phi \right)$, then there is a Borel partition $A = \bigcup_{n\geq 1}A_n$ and some $\set{\gamma_n}_{n\geq 1}$ such that for any $x\in A_n$, we have $\phi(x) = \gamma_n\cdot x$, meaning $B = \bigcup_{n\geq 1}\gamma_n\cdot A_n$.
\end{proof}

\begin{definition}
  A measure $\mu$ is called $\mathcal{R}$-ergodic if every $\mathcal{R}$-invariant Borel set is either null or co-null. The measure $\mu$ is ergodic with respect to the action of a group $\Gamma$ if it is ergodic for $\mathcal{R}\left( \Gamma\curvearrowright X \right)$.
\end{definition}
We discuss an example.

Let $\mu$ be the product measure on the space $X = 2^{\Gamma}$, where $\Gamma$ is a countably infinite group, and $2 = \set{0,1}$ assigns weight $1/2$ to each element. For each finite $S\subseteq \Gamma$, and map $s\colon S\rightarrow 2$, set
\begin{align*}
  \mathcal{N}_s &= \set{f | f|_{S} = s}.
\end{align*}
Then, the set $\mathcal{N}_s$ forms a clopen basis for $2^{\Gamma}$, and we may define $\mu\left( \mathcal{N}_s \right) = 2^{-\left\vert S \right\vert}$. Since
\begin{align*}
  \gamma\cdot \mathcal{N}_s &= \mathcal{N}_{\gamma\cdot s},
\end{align*}
we have that $\mu$ is shift-invariant.

In fact, we claim that $\mu$ is mixing, in that
\begin{align*}
  \lim_{n\rightarrow\infty} \mu\left( \gamma\cdot \left( A\cap B \right) \right) &= \mu\left( A \right)\mu\left( B \right)
\end{align*}
for any Borel $A,B\subseteq X$. Given any $A,B\subseteq X$ and $\ve > 0$, we may find finite unions of clopen sets $A'$ and $B'$ such that $\mu\left( A\triangle A' \right),\mu\left( B\triangle B' \right) < \ve$. In particular, this means we only need to show the mixing condition when $A$ and $B$ are finite unions of basic clopen sets. If $A$ is supported on $S$ and $B$ is supported on $T$, where $S,T$ are finite, then for all but finitely many $\gamma$, we have $\gamma\cdot S\cap T = \emptyset$, meaning $\gamma\cdot A$ and $B$ are independent, meaning
\begin{align*}
  \mu\left( \gamma\cdot A\cap B \right) &= \mu\left( \gamma\cdot A \right)\mu\left( B \right)\\
                                        &= \mu\left( A \right)\mu\left( B \right).
\end{align*}
\begin{definition}
  We say $\left( X,\mathcal{R} \right)$ and $\left( Y,\mathcal{S} \right)$ are Borel isomorphic if there is a Borel bijection $\pi\colon X\rightarrow Y$ such that $\left( x,y \right)\in \mathcal{R}$ if and only if $\left( \pi(x),\pi(y) \right)\in \mathcal{S}$.

  If $\mu$ and $\nu$ are invariant Borel probability measures on $X$ and $Y$ respectively, then we say they are almost everywhere Borel isomorphic if there are conull invariant Borel subsets $A\subseteq X$ and $B\subseteq Y$ and a Borel isomorphism $\pi\colon \left( A,\mathcal{R}|_{A} \right) \rightarrow \left( B,\mathcal{S}|_{B} \right)$ with $\pi_{\ast}\mu=\nu$.
\end{definition}
\begin{definition}
  We say two actions $\Gamma\curvearrowright X$ and $\Lambda\curvearrowright Y$ are \textit{orbit equivalent} if the respective orbit equivalence relations $ \mathcal{R}\left( \Gamma\curvearrowright X \right) $ and $\mathcal{R}\left( \Lambda\curvearrowright Y \right)$ are Borel isomorphic.

  If the actions of $\Gamma$ and $\Lambda$ are both measure-preserving actions on finite Borel measure spaces, then they are orbit equivalent if the equivalence relations are almost everywhere Borel isomorphic with $\pi_{\ast}\mu = \nu$.
\end{definition}
\subsection{Von Neumann Algebras of Equivalence Relations}%
We start by considering a type of ``mass transport principle'' on an equivalence relation $\mathcal{R}\subseteq X\times X$, where $\left( X,\mu \right)$ is some probability space. From now on, we will disregard null sets (i.e., ``every'' means ``almost every''). We will also assume that (almost) every orbit of $\mathcal{R}$ is infinite.
\begin{definition}
  If $\mathcal{R}\subseteq X\times X$ is an equivalence relation, and $\mathcal{W}\subseteq \mathcal{R}$ is Borel, then we define
  \begin{align*}
    \nu\left( \mathcal{W} \right) &= \int_{X}^{} \mu\left( \set{y\in X | \left( x,y \right)\in \mathcal{W}} \right)\:d\mu(x).
  \end{align*}
\end{definition}
Note that since $\mu$ is invariant under $\mathcal{R}$, we have that
\begin{align*}
  \int_{X}^{} \mu\left( \set{y\in X | \left( x,y \right)\in \mathcal{W}} \right)\:d\mu(x) &= \int_{X}^{} \mu\left( \set{x\in X | \left( x,y \right)\in \mathcal{W}} \right)\:d\mu(y).
\end{align*}
Note that if $f\colon X_1\rightarrow X_2$ is a Borel isomorphism, then there is a unique $\pi_{f}\colon L_{\infty}\left( X_1 \right)\rightarrow L_{\infty}\left( X_2 \right)$ given by $\pi_{f}\left( \phi \right)\left( x \right) = \phi\left( f^{-1}(x) \right)$.

Now, consider the space $L_2\left( \mathcal{R},\nu \right)$. If $\phi\in \left[ \left[ \mathcal{R} \right] \right]$, and $\xi\in L_2\left( \mathcal{R},\nu \right)$, define
\begin{align*}
  \left( u_{\phi}\xi \right)\left( x,y \right) &= \chi_{\operatorname{ran}\left( \phi \right)}(x)\xi\left( \phi^{-1}\left( x \right),y \right).
\end{align*}
That is,
\begin{align*}
  \left( u_{\phi}\xi \right)\left( x,y \right) &= \xi\left( \phi^{-1}(x),y \right)
\end{align*}
if $x\in \operatorname{ran}\left( \phi \right)$ and $0$ otherwise. The von Neumann algebra $L_{\infty}(X)$ acts on $L_2\left( \mathcal{R},\nu \right)$ by multiplication in the $x$ coordinate:
\begin{align*}
  \left( F\xi \right)\left( x,y \right) &= F\left( x \right)\xi\left( x,y \right).
\end{align*}
If $\phi\in \left[ \left[ \mathcal{R} \right] \right]$ and $F\in L_{\infty}\left( X \right)$, then $F_{\phi}\in L_{\infty}\left( X \right)$ can be defined by
\begin{align*}
  F_{\phi}(x) &= \chi_{\operatorname{ran}\left( \phi \right)}(x)F\left( \phi^{-1}\left( x \right) \right).
\end{align*}
That is, $F_{\phi}(x) = F\left( \phi^{-1}\left( x \right) \right)$ if $x\in \operatorname{ran}\left( \phi \right)$ and $0$ otherwise. We call this the left-regular representation of $\mathcal{R}$.

Similarly, it is possible to define the right-regular representation of $\mathcal{R}$ by taking $\left( v_{\phi}\xi \right)\left( x,y \right) = \1_{\operatorname{ran}\left( \phi \right)}(y)\xi\left( x,\phi^{-1}\left( y \right) \right)$.
\begin{proposition}
  If $\phi,\psi\in \left[ \left[ R \right] \right]$, the following hold:
  \begin{enumerate}[(i)]
    \item $u_{\phi}u_{\psi} = u_{\phi\psi}$;
    \item $u_{\phi}^{\ast} = u_{\phi^{-1}}$;
    \item $u_{\phi}^{\ast}u_{\psi} = \chi_{\operatorname{dom}\left( \phi \right)}$ and $u_{\phi}u_{\phi}^{\ast} = \chi_{\operatorname{ran}\left( \phi \right)}$;
    \item $u_{\phi}F = F_{\phi}u_{\phi}$ for any $F\in L_{\infty}\left( X \right)$.
  \end{enumerate}
\end{proposition}
\begin{definition}
  Define the von Neumann algebra $L\left( \mathcal{R} \right)\subseteq B\left( L_2\left( \mathcal{R},\nu \right) \right)$ to be the von Neumann algebra generated by the set $\set{u_{\phi} | \phi\in \left[ \left[ \mathcal{R} \right] \right]}$.

  Likewise, define $R\left( \mathcal{R} \right)\subseteq B\left( L_2\left( \mathcal{R},\nu \right) \right)$ to be the von Neumann algebra generated by $\set{v_{\phi} | \phi\in \left[ \left[ \mathcal{R} \right] \right]}$.
\end{definition}
Before we may start understanding the von Neumann algebra of such equivalence relations, we discuss the standard representation of a finite von Neumann algebra $\left( M,\tau \right)$.
\begin{proposition}
  Let $M$ be a finite von Neumann algebra with trace $\tau$. Then, the map $x\mapsto x^{\ast}$ extends to an anti-linear isometry $J\colon L_2\left( M,\tau \right)\rightarrow L_2\left( M,\tau \right)$ with $JMJ = M'\cap B\left( L_2\left( M,\tau \right) \right)$. Here, $L_2\left( M,\tau \right)$ refers to the GNS representation of $M$ with respect to the faithful state $\tau$.
\end{proposition}
\begin{proof}
  For any $x\in M$, we have
  \begin{align*}
    \norm{x^{\ast}}_{\tau}^2 &= \tau\left( xx^{\ast} \right)\\
                             &= \tau\left( x^{\ast}x \right)\\
                             &= \norm{x}_{\tau}^2.
  \end{align*}
  Thus, this extends to an anti-linear isometry $J\colon L_2\left( M,\tau \right)\rightarrow L_2\left( M,\tau \right)$. We have $ \iprod{J\xi}{J\eta} = \iprod{\xi}{\eta} $ for all $\xi,\eta\in L_2\left( M,\tau \right)$.

  For any $\xi\in L_2\left( M,\tau \right)$, define the unbounded operators $L_{\xi}^{0}\colon M1_{\tau}\rightarrow L_2\left( M,\tau \right)$ and $R_{\xi}^{0}\colon M1_{\tau}\rightarrow L_2\left( M,\tau \right)$ by
  \begin{align*}
    L_{\xi}^0\left( x1_{\tau} \right) &= \left( Jx^{\ast}J \right)\xi\\
    R_{\xi}^{0}\left( x1_{\tau} \right) &= x\xi.
  \end{align*}
  Here, $1_{\tau}$ refers to the cyclic vector for the representation $\tau$.

  If $\left( x_i \right)_i\in M$ and $\eta\in L_2\left( M,\tau \right)$ are such that $\norm{x_i}_{\tau}\rightarrow 0$ and $L_{\xi}^0\left( x_i1_{\tau} \right)\rightarrow\eta$, then for all $z\in M$, we have
  \begin{align*}
    \left\vert \iprod{\eta}{z} \right\vert &= \lim_{i} \left\vert \iprod{\left( Jx_i^{\ast}J \right)\xi}{z} \right\vert\\
                                           &= \lim_{i} \left\vert \iprod{\xi}{zx_i^{\ast}} \right\vert\\
                                           &\leq \lim_{i} \norm{\xi}_{\tau}\norm{z}_{\op}\norm{x_i}_{\tau}\\
                                           &= 0,
  \end{align*}
  meaning that $L_{\xi}^0$ is closable. Completing the graph gives rise to a closed operator $L_{\xi}$, and similarly $R_{\xi}^0$ is closable with corresponding operator $R_{\xi}$. We have that $L_{x1_{\tau}} = x$ for all $x\in M$.
\end{proof}
\section{Amenability and Hyperfiniteness}%
Our goal now is to show that non-atomic probability measure preserving ergodic actions of amenable groups are orbit equivalent. This is a conclusion of the combination of two theorems; a theorem of Dye says that any two non-atomic probability measure-preserving ergodic actions of $\Z$ are orbit equivalent, and a theorem of Ornstein and Weiss says that any probability measure-preserving action of an amenable group is orbit equivalent to one of $\Z$. This will eventually yield the celebrated Connes--Feldman--Weiss theorem, which states the following.
\begin{theorem}
  Let $\mathcal{R}$ be a countable Borel equivalence relation on $X$, and let $\mu$ be an $\mathcal{R}$-quasi-invariant probability measure. If $\mathcal{R}$ is $\mu$-amenable, then $\mathcal{R}$ is almost everywhere hyperfinite.
\end{theorem}
We will assume command of understanding of amenability in the case of groups, which is discussed in depth in \href{https://ai.avinash-iyer.com/Classes_and_Homework/College/Y4/Honors\%20Thesis/Amenability\%20Text/amenability.pdf}{this document}.
\subsection{Hyperfiniteness}%
We start by studying equivalence relations induced by $\Z$-actions.
\begin{definition}
  If $\mathcal{R}$ is a Borel equivalence relation on $X$, we say $\mathcal{R}$ is \textit{smooth} if it admits a family $\set{B_n}_{n\in \N}$ of Borel subsets of $X$ such that for all $x,y\in X$, $\left( x,y \right)\in \mathcal{R}$ if and only if, for all $n\in \N$, $x\in B_n$ if and only if $y\in B_n$.
\end{definition}
Via the maps $x\mapsto \set{\chi_{B_n}\left( x \right)}_{n\in \N}$, we see that this definition says $\mathcal{R}$ is smooth if and only if there is a Borel function $\phi\colon X\rightarrow Y$ with $Y$ a standard Borel space such that for all $x,y\in X$, we have $\left( x,y \right)\in \mathcal{R}$ if and only if $\phi(x) = \phi(y)$.
\begin{definition}
  If $\mathcal{R}$ is a Borel equivalence relation, we define $X/\mathcal{R}$ to be the set of equivalence classes of $\mathcal{R}$ equipped with the quotient Borel structure, wherein $A\subseteq X/\mathcal{R}$ is Borel if and only if $\bigcup A$ is Borel in $X$.
\end{definition}
\begin{proposition}
  A countable Borel equivalence relation $\mathcal{R}$ is smooth if and only if $X/\mathcal{R}$ is standard Borel.
\end{proposition}
\begin{proof}
  Let $\phi\colon X\rightarrow Y$ be a surjection that gives the smoothness of $\mathcal{R}$, and let $ \varphi $ be the induced bijection from $X/\mathcal{R}\rightarrow Y$. It suffices to verify that $\varphi$ induces an isomorphism o the quotient Borel structure $X/\mathcal{R}$ with the standard Borel structure of $Y$. Since $\phi$ is countable-to-one, we have that $\phi$ maps Borel sets to Borel sets, meaning that an $\mathcal{R}$-invariant set $B$ is Borel if and only if $ \varphi\left( B \right) = \phi(B) $ is Borel.

  In the reverse direction, if the quotient Borel structure on $X/\mathcal{R}$ is standard Borel, then there is a countable family of Borel sets $\set{B_n}_{n\in \N}$ in the quotient Borel structure that separates points. Yet, any such family induces a Borel separating family for $\mathcal{R}$.
\end{proof}
\begin{definition}
  A \textit{complete section} for $\mathcal{R}$ is a set $B\subseteq X$ that intersects every equivalence class in $\mathcal{R}$.

  A \textit{transversal} for $\mathcal{R}$ is a set $B\subseteq X$ that intersects every equivalence class in $\mathcal{R}$ exactly once.

  A \textit{selector} for $\mathcal{R}$ is a function $f\colon X\rightarrow X$ with $\operatorname{graph}\left( f \right)\subseteq \mathcal{R}$ and $f(X)\subseteq X$ is a transversal.
\end{definition}
A Borel equivalence relation admits a Borel transversal if and only if it admits a Borel selector; if it admits a Borel transversal, then it is smooth (but this is not true in reverse).
\begin{proposition}
  If $\mathcal{R}$ is a \textit{countable} smooth equivalence relation, then $\mathcal{R}$ admits a Borel selector. Moreover, if all the classes of $\mathcal{R}$ are of size $n\in \N\cup\set{\infty}$, then there is a sequence $\set{f_i}_{i < n}$ of Borel selectors for $\mathcal{R}$ whose images partition $X$.
\end{proposition}
\begin{proof}
  Let $\phi\colon X\rightarrow Y$ be a surjection that implements the smoothness of $\mathcal{R}$, and define a relation $\mathcal{S}\subseteq Y\times X$ by saying $\left( y,x \right)\in \mathcal{S}$ if and only if $\phi(x)=y$.

  Since $\mathcal{S}$ is Borel and has countable sections, it follows from the \href{https://en.wikipedia.org/wiki/Countable_Borel_relation#The_Luzin\%E2\%80\%93Novikov_theorem}{Lusin--Novikov Theorem} that there is a Borel uniformization $f\colon Y\rightarrow X$ of $\mathcal{S}$. It follows that $f\circ\phi$ is our desired Borel selector.

  Now, if all the classes of $\mathcal{R}$ are of size $n\leq \aleph_0$, there are then sequences $\set{f_i}_{i < n}$ of Borel uniformizations of $\mathcal{S}$ with disjoint ranges whose union is $X$, so $\set{f_i\circ\phi}_{i < n}$ is a sequence of Borel selectors whose images partition $X$.
\end{proof}
\nocite{ii1_factors_houdayer,topics_in_orbit_equivalence,von_neumann_algebras_peterson}
\printbibliography
\end{document}
