\documentclass[11pt]{article}

%\usepackage{psfrag}%to make pictures work nicely?
\usepackage{amsfonts,enumerate}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epsfig, psfrag}
\usepackage{graphicx}
\usepackage{color}
\usepackage{anysize}

\marginsize{1.25in}{1.25in}{.5in}{1.25in}
\parindent=0cm

\input{makros}

\begin{document}
\begin{center}
{\bf \Large Math 395 \\[0.1in]Homework 1 \\[0.1in]
Due: 2/1/2024}\\[.25in]
{\bf Name:} {Avinash Iyer}\\[0.15in]
{\bf Collaborators:} {\underline{\hspace*{4.5in}}} \\
\end{center}

\begin{enumerate}

\item Let $S$ be the subset of $\Mat_{2}(\bfR)$  be the set consisting of matrices of the form $\bmat a & a \\ b & b \emat$. 
\begin{enumerate}
\item Prove that $S$ is a ring.\\
  \begin{description}
    \item[Proof:] We will show that $S$ is a ring by using the ring axioms.
      \begin{itemize}
        \item Closure of Addition:
          \begin{align*}
            \bmat a & a \\ b&b\emat + \bmat c&c\\d&d\emat &= \bmat a+c & a+c\\b+d & b+d\emat.
          \end{align*}
        \item Additive Identity:
          \begin{align*}
            \bmat a&a\\b&b\emat + \bmat 0&0\\0&0\emat &= \bmat a+0 & a+0\\b+0 & b+0\emat\\
                   &= \begin{bmatrix}a&a\\b&b\end{bmatrix}
          \end{align*}
        \item Additive Inverse:
          \begin{align*}
            \begin{bmatrix}a&a\\b&b\end{bmatrix} + \begin{bmatrix}-a&-a \\ -b&-b\end{bmatrix} &= \begin{bmatrix}a-a&a-a\\b-b&b-b\end{bmatrix}\\
                            &= \begin{bmatrix}0&0\\0&0\end{bmatrix}
          \end{align*}
        \item Associativity of Addition:
          \begin{align*}
            \left(\begin{bmatrix}a&a\\b&b\end{bmatrix} + \begin{bmatrix}c&c\\d&d\end{bmatrix}\right) + \begin{bmatrix}e&e\\f&f\end{bmatrix} &= \begin{bmatrix}(a+c)+e & (a+c)+e\\(b+d)+f & (b+d)+f\end{bmatrix}\\
                                  &= \begin{bmatrix}a+(c+e) & a+(c+e)\\b+(d+f) & b+(d+f)\end{bmatrix}\\
                                  &= \begin{bmatrix}a&a\\b&b\end{bmatrix} + \left( \begin{bmatrix}c&c\\d&d\end{bmatrix} + \begin{bmatrix}e&e\\f&f\end{bmatrix}\right).
          \end{align*}
        \item Commutativity of Addition:
          \begin{align*}
            \begin{bmatrix}a&a\\b&b\end{bmatrix} + \begin{bmatrix}c&c\\d&d\end{bmatrix} &= \begin{bmatrix}a+c&a+c\\b+d&b+d\end{bmatrix}\\
                            &= \begin{bmatrix}c+a&c+a\\d+b&d+b\end{bmatrix}\\
                            &= \begin{bmatrix}c&c\\d&d\end{bmatrix} + \begin{bmatrix}a&a\\b&b\end{bmatrix}.
          \end{align*}
        \item Closure of Multiplication:
          \begin{align*}
            \begin{bmatrix}a&a\\b&b\end{bmatrix}\cdot \begin{bmatrix}c&c\\d&d\end{bmatrix} &= \begin{bmatrix}ac+ad & ac+ad\\bc+bd\\bc+bd\end{bmatrix}.
          \end{align*}
        \item Since multiplication in
      \end{itemize}
  \end{description}
\item Show that $J = \bmat 1 & 1 \\ 0 & 0 \emat$ is a right identity in $S$, i.e., $AJ = A$ for all $A \in \Mat_2(\bfR)$. 
\item Show that $J$ is not a left identity for $S$, i.e., there is an element $B \in S$ so that $JB \neq B$. 
\end{enumerate}

\item Show that the subset $S = \{[0]_{18}, [3]_{18}, [6]_{18}, [9]_{18}, [12]_{18}, [15]_{18}\}$ is a subring of $\bfZ/18\bfZ$.  Does $S$ have an identity?

\item Define a new addition and multiplication on $\bfZ$ by 
\begin{align*}
a\oplus b&= a+b-1 \\
a\odot b&= ab - (a+b)+2.
\end{align*}
Prove that under these operations $\bfZ$ is an integral domain. 

\item Let $R$ be a ring and define $\textrm{$Z(R) = \{a \in R: ar = ra$ for every $r \in R$}\}$. Prove that $Z(R)$ is a subring of $R$. It is referred to as the center of $R$. 

\item Let $R$ be a ring and fix an element $x \in R$.  Show that the set $\{rx: r \in R\}$ is a subring of $R$. 

\item Let $S$ and $T$ be subrings of a ring $R$. 
\begin{enumerate}
\item Is $S\cap T$ a subring of $R$?  Justify your answer with a proof or counterexample.
\item Is $S\cup T$ a subring of $R$?  Justify your answer with a proof or counterexample.
\end{enumerate}

\item Let $A = \bmat a & b \\ c & d \emat \in \Mat_2(F)$ where $F$ is a field. 
\begin{enumerate}
\item Prove that $A$ is invertible if and only if $ad-bc \neq 0_{F}$. 
\item Prove that $A$ is a zero divisor if and only if $ad-bc = 0_{F}$. 
\item If instead we consider a matrix $A \in \Mat_2(\bfZ)$, do the same conclusions hold?  If so, prove them.  If not, adjust them to true statements and prove those statements.
\end{enumerate}





\end{enumerate}

\end{document} 
