\documentclass[10pt]{mypackage}

% sans serif font:
%\usepackage{cmbright}
%\usepackage{sfmath}
%\usepackage{bbold} %better blackboard bold

\usepackage{homework}
%\usepackage{notes}
\usepackage{newpxtext,eulerpx,eucal}
\renewcommand*{\mathbb}[1]{\varmathbb{#1}}

\fancyhf{}
\rhead{Avinash Iyer}
\lhead{Differential Topology: Problem Set 5}

\setcounter{secnumdepth}{0}

\begin{document}
\RaggedRight
\begin{problem}[Problem 1]
  Prove that smooth homotopy and smooth isotopy are equivalence relations.
\end{problem}
\begin{solution}
  If $f\colon M\rightarrow N$ is a smooth map, then we can define a smooth homotopy $F\colon M\times [0,1]\rightarrow N$ by taking $F\left( \cdot,t \right) = f$. If $f$ is a diffeomorphism, then this is a smooth isotopy. Thus, this relation is reflexive.\newline

  The relation is symmetric since, if $f$ and $g$ are smoothly homotopic (isotopic), then $F^{\ast}\colon M\times [0,1]\rightarrow N$, given by $F^{\ast}\left( \cdot,t \right) = F\left( \cdot,1-t \right)$ is a composition of smooth maps, hence smooth.\newline

  The relation is transitive since, if $F\colon M\times [0,1]\rightarrow N$ is a homotopy (isotopy) from $f$ to $g$, and $G\colon M\times [0,1]\rightarrow N$ is a homotopy (isotopy) from $g$ to $h$, then we may find a homotopy from $f$ to $h$ by taking
  \begin{align*}
    H\left( \cdot,t \right) &= \begin{cases}
      F\left( \cdot,2t \right) & 0 \leq t \leq \frac{1}{2}\\
      G\left( \cdot,2t-1 \right) & \frac{1}{2}\leq t \leq 1.
    \end{cases}
  \end{align*}
  This is a smooth map since the derivatives of all orders for $F$ and $G$ agree at $t = \frac{1}{2}$.
\end{solution}
\begin{problem}[Problem 2]
  Prove that if $M$ is connected, then for all pairs $p$ and $q$ of points on $M$, there is a diffeomorphism $f$ of $M$ such that $f(p) = q$ and $f$ is isotopic to the identity.
\end{problem}
\begin{solution}
  We know that the diffeomorphism group, $ \operatorname{diff}\left( M \right) $, is transitive whenever $M$ is connected, so there is a diffeomorphism $f\colon M\rightarrow M$ such that $f(p) = q$. Now, if $p$ and $q$ are in the same Euclidean chart, $\left( U,\varphi \right)$, where $\varphi(p) = 0$ and $\varphi(q) = ax_1$, then we may find the desired isotopy to the identity by taking
  \begin{align*}
    F\colon M\times [0,1]\rightarrow M
  \end{align*}
  to be given by
  \begin{align*}
    F\left( \cdot,t \right) &= f_{t},
  \end{align*}
  where $f_{t}$ is a diffeomorphism such that $\varphi\circ f_t(p) = atx_1$.\newline

  Now, if $p$ and $q$ are not in the same chart, then since $M$ is connected, there is a finite chain of $k$ intersecting Euclidean charts that we may compose with each other such that we get our diffeomorphism between $p$ and $q$. Dividing $ \left[ 0,1 \right] $ into intervals of length $1/k$, we may then find isotopies from the identity to the diffeomorphism mapping $p$ to the $\ell$-th intersection point along in this chain as we showed for the case where both $p$ and $q$ are in the same chart. By chaining these isotopies together, we get the isotopy between $f$ and the identity.
\end{solution}
\begin{problem}[Problem 3]
  Suppose $M$ is compact and has no boundary, and that $M$ and $N$ have the same dimension. Let $f$ and $g$ be homotopic maps from $M$ to $N$. Suppose $p\in N$ is a regular value for both $f$ and $g$. Prove that $ \left\vert f^{-1}(p) \right\vert = \left\vert g^{-1}\left( p \right) \right\vert $ modulo $2$.
\end{problem}
\begin{solution}
  Let $F\colon M\times [0,1]\rightarrow N$ be a smooth homotopy with $F\left( \cdot,0 \right) = f$ and $F\left( \cdot,1 \right) = g$. If $p\in N$ is a regular value for $F$ (in addition to one for $f$ and $g$), it follows that $F^{-1}(p)$ is a $1$-manifold subset of $M\times [0,1]$, where $F^{-1}(p)\cap \left( M\times \set{0} \right) = f^{-1}(p)\times \set{0}$, and $F^{-1}(p)\cap \left( M\times \set{1} \right) = g^{-1}(p)\times \set{1}$. Since the boundary of $M\times \left[ 0,1 \right]$ must contain an even number of points (as every $1$-submanifold with boundary of $M\times [0,1]$ must have both of its boundary points touch the boundary of $M\times \left[ 0,1 \right]$, which are $0$ and $1$), we must have $\left\vert f^{-1}(p) \right\vert + \left\vert g^{-1}(p) \right\vert \equiv 0$ modulo $2$, so that $ \left\vert f^{-1}(p) \right\vert = \left\vert g^{-1}(p) \right\vert $.\newline

  Suppose $y$ is not a regular value for $F$. Since $M\times [0,1]$ is compact, and $F$ is continuous, it follows that, by Sard's Theorem, $y$ is part of a closed, measure-zero subset of $N$. In particular, for any neighborhood of $y$, there is a regular value for $F$ within this neighborhood. Next, we observe that, for a sufficiently small open neighborhood $V$ of $y$, the number of regular points mapping to $y$ does not change, as the map $x\mapsto \left\vert F^{-1}(x) \right\vert$ is continuous and discrete-valued (for the open subset of regular values for $F$). Thus, on $V$, we may find $q\in V$ such that $\left\vert F^{-1}(q) \right\vert$ is constant, and thus $\left\vert f^{-1}(y) \right\vert + \left\vert g^{-1}(y) \right\vert$ is even, hence are equal to each other modulo $2$.
\end{solution}
\begin{problem}[Problem 4]
  Prove that for $M,N,f$ as in the previous exercise, $\left\vert f^{-1}(p) \right\vert \equiv \left\vert f^{-1}(q) \right\vert$ modulo $2$ for all regular values $p$ and $q$ of $f$, using the previous exercises.
\end{problem}
\begin{solution}
  There is a diffeomorphism $\varphi\colon N\rightarrow N$ of $N$ such that $\varphi\left( p \right) = q$ and $\varphi$ is isotopic to the identity, as shown in the solution to Problem 2. In particular, this means that $\varphi\circ f\colon M\rightarrow N$ is homotopic to $f\colon M\rightarrow N$, meaning that $\left\vert f^{-1}(p) \right\vert = \left\vert \left( \varphi\circ f \right)^{-1}(q) \right\vert = \left\vert f^{-1}(q) \right\vert$, with the latter equality following from Problem 3.
\end{solution}
\begin{problem}[Problem 5]
  Let $M$ be compact and have no boundary. Let $p\in M$, and $f\colon M\rightarrow M$ be defined by $f(x) = p$. Prove that $f$ is not homotopic to the identity map.
\end{problem}
\begin{solution}
  The identity map, $ \operatorname{id} $, is a diffeomorphism of $M$, so $\operatorname{id}^{-1}\left( q \right) = \set{q}$ for all $q\in M$. Notice that, for $q\neq p$, $f^{-1}\left( q \right) = \emptyset$, meaning that $q\neq p$ are vacuously regular values for $f$; since these inverse images have cardinality zero, it follows that $f$ and $ \operatorname{id} $ cannot be homotopic, since we established in Problem 3 that the cardinality of the preimage of a regular value is invariant under homotopy.
\end{solution}
\begin{problem}[Problem 6]
  Let $f\colon M\rightarrow N$ be smooth and oriented, with $M$ compact and boundaryless and $M$ and $N$ of the same dimension. Show that if $M = \partial W$ for some smooth manifold $W$, and $f$ extends smoothly to $W$, then for all $p\in N$ a regular value, we have $\operatorname{deg}\left( f,p \right) = 0$.
\end{problem}
\begin{solution}
  Let $\hat{f}$ be the smooth extension of $f$ to $W$. Since $p$ is a regular value for $\hat{f}$, there are points $q_1$ and $q_2$ on $M$ such that $\hat{f}^{-1}\left( p \right)$ contains a path $\gamma$ starting at $q_1$ and ending at $q_2$; this follows from the regular value theorem and the fact that $W$ is a manifold of dimension $n + 1$ when $M$ is a manifold of dimension $N$. In particular, we may cover $\gamma$ by finitely many charts that connect $q_1$ to $q_2$.\newline

  Since $W$ is oriented, we may select orientations such that all the interior points of $\gamma$ remain the same orientation in $W$; yet, if $\partial_{n+1}$ denotes the tangent vector at $q_1$ that allows for positive orientation at $q_1$, then upon following this path, the sign of the image of $\partial_{n+1}$ under the family of composed differential maps flips, as we go from an ``inward'' orientation at $q_1$ to an ``outward'' orientation right as $\gamma$ approaches $q_2$. This gives that the degree of $\hat{f}$ when it comes to the pair $\left( q_1,q_2 \right)$ is zero. This holds for all such pairs $\left( q_i,q_{i+1} \right)$ that land on $M$, meaning that $ \operatorname{deg}\left( f,p \right) = 0 $.
\end{solution}
\begin{problem}[Problem 7]
  Let $M$ and $N$ be as in the previous exercise. Prove that if $f$ and $g$ are homotopic, and $p\in N$ is a common regular value for both, then $ \operatorname{deg}\left( f,p \right) = \operatorname{deg}\left( g,p \right) $.
\end{problem}
\begin{solution}
  If $F\colon M\times [0,1]\rightarrow N$ is a homotopy from $f$ to $g$, then we see that for any regular values $p$ for $F$, $F^{-1}\left( p \right)$ is a $1$-manifold with two boundary points, so that these $1$-manifolds intersect $M\times \set{0}$ or $M\times \set{1}$. Observe that the orientation at $M\times \set{1}$ is negative to that at $M\times \set{0}$, meaning that $ \operatorname{deg}\left( F,p \right) = 0 = \operatorname{deg}\left( f,p \right) - \operatorname{deg}\left( g,p \right)$.
\end{solution}
\begin{problem}[Problem 8]
  Show that $ \operatorname{deg}\left( f,p \right) $ is independent of the choice of regular value $p$, so that the \textit{degree}, $\operatorname{deg}\left( f \right)$, can be defined. Show that homotopic maps have equal degrees.
\end{problem}
\begin{solution}
  We have shown in Problem 7 that, if $p$ is a common regular value for homotopic maps $f$ and $g$, then $ \operatorname{deg}\left( f,p \right) = \operatorname{deg}\left( g,p \right) $. Additionally, we have shown that, if $p$ and $q$ are regular values for $f$, then there is a diffeomorphism $\varphi$ of $N$ that maps $p$ to $q$ that is isotopic to the identity; we may then compose this isotopy with $f$ such that we get a homotopy between $f$ and $\varphi\circ f$; this means that $ \operatorname{deg}\left( f,p \right) = \operatorname{deg}\left( \varphi\circ f,q \right) $, so that the degree of a map $f$ is independent of the regular value.\newline

  If $f$ and $g$ are homotopic to each other, it follows that for each regular value in common, $f$ and $g$ have the same degree with respect to this regular value; since any regular value in common for $f$ and $g$ admits a diffeomorphism isotopic to the identity, it follows that both $f$ and $g$ have the same degree for all regular values in common. Since any regular value for one function is arbitrarily close to a regular value for both functions, it follows that $\operatorname{deg}\left( f \right) = \operatorname{deg}\left( g \right)$.
\end{solution}
\begin{problem}[Problem 9]
  Prove that for a sphere $S^{n}$ viewed as the unit sphere in $\R^{n+1}$, the antipodal map $x\mapsto -x$ has degree $-1$ if and only if $n$ is even.
\end{problem}
\begin{solution}
  Let $x\in S^{n}\subseteq \R^{n+1}$. We view $S^{n}$ as the boundary of the unit ball $B\left( 0,1 \right)\subseteq\R^{n+1}$; a point $p\in S^{n}$ then has an orientation defined by
  \begin{align*}
    \left( -\pd{}{x_{n+1}},\pd{}{x_{1}},\dots,\pd{}{x_{n}} \right).
  \end{align*}
  The map $x\mapsto -x$ in $\R^{n+1}$ then flips signs for all the tangent vectors on this orientation, giving
  \begin{align*}
    \left( \pd{}{x_{n+1}},-\pd{}{x_1},\dots,-\pd{}{x_{n}} \right) &= \left( -1 \right)^{n+1} \left( -\pd{}{x_{n+1}},\pd{}{x_1},\dots,\pd{}{x_n} \right).
  \end{align*}
  The degree of $x\mapsto -x$ is thus negative if and only if $n+1$ is odd, meaning it holds if and only if $n$ is even.
\end{solution}
\begin{problem}[Problem 10]
  Prove that the sphere $S^{n}$ admits a nowhere-vanishing vector field if and only if $n$ is odd.
\end{problem}
\begin{solution}
  In order to construct a smooth homotopy $F\colon S^{n}\times [0,1]\rightarrow S^{n}$ between the identity and antipodal map, we want $F\left( p,0 \right) = p$, $F\left( p,1 \right) = -p$, and $ \norm{F(p,t)}^2 = 1 $ for all $p$ and all $t$. We start by taking
  \begin{align*}
    F\left( p,t \right) &= p\cos\left( \pi t \right) + y(p)\sin\left( \pi t \right);
  \end{align*}
  and taking the dot product of $F$ with itself to yield
  \begin{align*}
    \norm{F\left( p,t \right)}^2 &= \iprod{p\cos\left( \pi t \right) + y(p)\sin\left( \pi t \right)}{ p\cos\left( \pi t \right) + y(p)\sin\left( \pi t \right) }\\
                                 &= \cos^2\left( \pi t \right) + \norm{y(p)}^2\sin^2\left( \pi t \right) + \iprod{p}{y(p)} \sin\left( 2\pi t \right)\\
                                 &= 1.
  \end{align*}
  Ideally, we desire $ \iprod{p}{y(p)} = 0 $, and $ \norm{y(p)}^2 = 1 $ for all $p\in S^{n}$. This entails the existence of a smooth map between $S^{n}$ and $S^{n}$ that maps $p$ to a vector orthogonal to $p$. Defining a smooth vector field on $S^{n}$ in this fashion, we find that such a vector field is necessarily nowhere-vanishing. This implies that the existence of a nowhere-vanishing vector field implies that the antipodal map is smoothly homotopic to the identity.\newline

  Meanwhile, we have shown in Problem 9 that, when $n$ is even, the degree of the antipodal map is $-1$, while the degree of the identity map is always $1$, meaning that when $n$ is even, the identity map cannot be smoothly homotopic to the identity, meaning there does not exist a nowhere-vanishing vector field when $n$ is even.
\end{solution}
\end{document}
